Police Shootings and Racism in America

### 2020-10-16 submissionii.Rmd
thinking bout model...

```{r clean-all}
all <- all %>% 
  select(-c("Date", "NatureOfStop", "Notes", "SubjectAge", "NumberOfShots", "Department", "FullNarrative", "fdate", "month", "day", "b", "l", "w", "a", "tr", "AvgAge", "VA", "F", "nshots", "sit"))

>>>>

```{r clean-all}
all <- all %>% 
  select(-c("Date", "NatureOfStop", "Notes", "SubjectAge", "NumberOfShots", "Department", "FullNarrative", "fdate", "month", "day", "tr", "AvgAge", "VA", "F", "nshots", "sit"))
